Automated Topic Naming

### 2012-04-06 ese/ese.tex
- [ ] There appear to be some discrepancies in numbers.          According to Table 2, there were 640 topics in Pg. 20 topics          per 30-day windo 32 30-day windows for Pg, yet the time          period appears to contain fewer such windows.  For the other          two projects the numbers of topics are not even divisible          by 20. Some clarification would help. It appears that Pg has          625 of 640 topics with at least two labels: testability and          correctness based on exp1. It may be worth giving he reader          some idea about how many topics have exactly one label

A topic analysis tool such as LDA will try to find $N$ independent
word distributions within the word distributions of all input
messages. 
If there are not $N$ independent word distributions, the topics
produced tend to be duplicates of each other, that is, they share the
top terms. During this study we found that if we used a value of 20
for $N$, duplicate topics were infrequent in MaxDB and MySQL. The
PostgreSQL study was added later and we followed the same methodology
to extract topics fro PostgreSQL, the choice of $N$ = 20 was not
necessarily the optimal choice for PostgreSQL.
Linear combinations of these $N$ word distributions are meant to represent and recreate the word distributions of any of the original messages. In other words, these topics are cross-cutting collections of words relevant to one or more of our commit messages. 
LDA extracts topics in an unsupervised manner; the algorithm relies
solely on the source data and word distributions of messages, with no human intervention.
%We applied Blei's LDA implementation~\cite{Blei2003} against the word distributions of these commits, and generated lists of topics per period.

@@

\subsection{Analysis of the Semi-Unsupervised Labelling}
% Did a little validation here
Table \ref{tbl:wordlist} shows how many topics were labelled for
MaxDB, MySQL and PostgreSQL.  Notice how PostgreSQL had far fewer
unlabelled topics, PostgreSQL also was under going far more
development as we evaluated 7744 PostgreSQL commits versus 8664 MaxDB
commits and 6223 MySQL commits. 
In terms of change-log comment words PostgreSQL had 164724, while
MaxDB had 68203, and MySQL had 101081. This implies there were
more PostgreSQL
terms for the topic analyzer to produce topics with.
And thus we suspect that PostgreSQL topics were
flooded with many terms, indicating that perhaps we needed more than 20 topics per month
for PostgreSQL, as this result indicates there is a lot of overlap in
the topics.

>>>>

A topic analysis tool such as LDA will try to find $N$ independent
word distributions within the word distributions of all input
messages. 
If there are not $N$ independent word distributions, the topics
produced tend to be duplicates of each other, that is, they share the
top terms. During this study we found that if we used a value of 20
for $N$, duplicate topics were infrequent in MaxDB and MySQL. 
Sometimes LDA produces topics that have a
very low association to documents, in this paper we removed topics
that
exhibit very low document association. Our threshold for
topic inclusion was that a topic needed at least 1
document with a gamma (the variational
posterior Dirichlet~\cite{Blei2003} of a topic to a document, similar
to an association weight) of $1.0$ or greater.
The
PostgreSQL study was added later and we followed the same methodology
to extract topics fro PostgreSQL, the choice of $N$ = 20 was not
necessarily the optimal choice for PostgreSQL.
Linear combinations of these $N$ word distributions are meant to represent and recreate the word distributions of any of the original messages. In other words, these topics are cross-cutting collections of words relevant to one or more of our commit messages. 
LDA extracts topics in an unsupervised manner; the algorithm relies
solely on the source data and word distributions of messages, with no human intervention.
%We applied Blei's LDA implementation~\cite{Blei2003} against the word distributions of these commits, and generated lists of topics per period.

@@

\subsection{Analysis of the Semi-Unsupervised Labelling}
% Did a little validation here
Table \ref{tbl:wordlist} shows how many topics were labelled for
MaxDB, MySQL and PostgreSQL.  
The total topics are often less than 20 times the number of months
studied because in some months there was not enough data for LDA to
extract 20 actual topics as some topics were not actually strongly
associated with any documents. 
Notice how PostgreSQL had far fewer
unlabelled topics, PostgreSQL also was under going far more
development as we evaluated 7744 PostgreSQL commits versus 8664 MaxDB
commits and 6223 MySQL commits. 
In terms of change-log comment words PostgreSQL had 164724, while
MaxDB had 68203, and MySQL had 101081. This implies there were
more PostgreSQL
terms for the topic analyzer to produce topics with.
And thus we suspect that PostgreSQL topics were
flooded with many terms, indicating that perhaps we needed more than 20 topics per month
for PostgreSQL, as this result indicates there is a lot of overlap in
the topics.
